surfing

### 2021-05-15 inst/surfing.Rmd
typos

```{r}
surfing_table <- read.table("wct_table2019.txt",header=TRUE)
options(width=100)
surfing_table
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
QS <- rownames(surfing_table)[c(23:33,35:36)]
QS
```

@@

>>>>

```{r}
surfing_table <- read.table("wct_table2019.txt",header=TRUE)
nationality <- function(surfers){surfing_table$nation[rownames(surfing_table) %in% surfers]}
```

```{r}
type <- read.table("venuetypes2019.txt",header=TRUE)
type
beachtype <- function(venue){type$beachtype[which(type$comp==venue)]}
beachtype("wct05")
beachtype("wct06")

options(width=100)
surfing_table
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
QS <- rownames(surfing_table)[c(23:33,35:36)]
QS
```

@@

# Brazilian null

One suggestion is that Brazilians do worse on reef break and better on
point and beach break beaches.  We now assess the null that Brazilians
perform equally well on all types of beaches.

```{r surfing2, cache=TRUE}
surfing2 <- hyper2()
for(v in o){
   venue <- v[1]  # first entry is venue
   r <- v[-1] 
   numberretained <- sum(!(r %in% remove))
   if(numberretained > 1){
     r <- r[!(r %in% remove)]
     jj <- race(r)
     surfers <- pnames(jj)
     if(any(nationality(surfers) == "BRA")){
       if((beachtype(venue)=="point") | (beachtype(venue) == "beach")){
         jj %<>% pwa(surfers[nationality(surfers)=="BRA"],"Brazilian_beachtype")
       }    	     
     } 
     surfing2 %<>% sum(jj)
   }
}	
summary(surfing2)
```

```{r surfing2max, cache=TRUE}
maxp(surfing2)
specificp.gt.test(surfing2,"Brazilian_beachtype",0)
```

```{r profsuppcalcsurfing2, cache=TRUE}
p <- seq(from=0.001,by=0.001,len=10)
l <- profsupp(surfing2,"Brazilian_beachtype",p)
```

```{r}
plot(p,l)
```
